Place of death in NRS COVID-19 deaths

### 2021-08-18 covid_nrs_place_of_death_visualisations.Rmd
added a graph showing absolute number of deaths by place over time ending in 2020

```{r}
(figure_number_of_deaths_by_place_by_year <-
  bind_rows(
    proportions_of_historical_deaths_by_place %>% filter(year==2019) %>% mutate(covid_status = "Non Covid-19 deaths"),  # add extra rows of 2019 data for plotting line between 2019 and 2020
    proportions_of_historical_deaths_by_place %>% mutate(covid_status = "All deaths"),
    proportions_of_current_non_covid_deaths_by_place %>% mutate(covid_status = "Non Covid-19 deaths"),
    proportions_of_current_deaths_by_place %>% mutate(covid_status = "All deaths")
  ) %>%
  filter(!place_of_death %in% c("All","Other")) %>%  # don't show Other
  # filter(year != 2021) %>%  # don't include 2021
  mutate(
    place_of_death = factor(x = place_of_death, levels = order_of_place_of_death_levels[c(1,3,2,4)])   # move home to 2nd position to match order in plot
    ) %>%
  ggplot(., aes(x=year, y=number_of_deaths, colour = place_of_death)) +
  geom_line(data = . %>% filter(covid_status == "All deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_line(data = . %>% filter(covid_status == "Non Covid-19 deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_point(data = . %>% filter(!covid_status=="Non Covid-19 deaths" | !year==2019)) +
  geom_text(data = . %>% filter(year==2016) %>% mutate(y_pos = c(3.1e4, 1.1e4, 1.8e4)), aes(y = y_pos, label = place_of_death), hjust = 0) +
  geom_text(data = ~filter(.x, year==2021), aes(x=2021.1, y=y, label="*"), inherit.aes = FALSE) +
  scale_colour_viridis_d(option="C", end = 0.8, guide = FALSE) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_x_continuous(breaks = 2015:2021) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.box="vertical",
    legend.margin=margin()
    ) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ","), limits = c(0, NA)) +
  labs(
    x = "Year", y = "Deaths (N)",
    subtitle = paste0("* ",only_2021_text),
    caption = paste0(c(death_registrations_text,source_nrs_text), collapse="\n")
  ) +
  NULL
)

@@

>>>>

```{r}
(figure_number_of_deaths_by_place_by_year <-
  bind_rows(
    proportions_of_historical_deaths_by_place %>% filter(year==2019) %>% mutate(covid_status = "Non Covid-19 deaths"),  # add extra rows of 2019 data for plotting line between 2019 and 2020
    proportions_of_historical_deaths_by_place %>% mutate(covid_status = "All deaths"),
    proportions_of_current_non_covid_deaths_by_place %>% mutate(covid_status = "Non Covid-19 deaths"),
    proportions_of_current_deaths_by_place %>% mutate(covid_status = "All deaths")
  ) %>%
  filter(!place_of_death %in% c("All","Other")) %>%  # don't show Other
  # filter(year != 2021) %>%  # don't include 2021
  mutate(
    place_of_death = factor(x = place_of_death, levels = order_of_place_of_death_levels[c(1,3,2,4)])   # move home to 2nd position to match order in plot
    ) %>%
  ggplot(., aes(x=year, y=number_of_deaths, colour = place_of_death)) +
  geom_line(data = . %>% filter(covid_status == "All deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_line(data = . %>% filter(covid_status == "Non Covid-19 deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_point(data = . %>% filter(!covid_status=="Non Covid-19 deaths" | !year==2019)) +
  geom_text(data = . %>% filter(year==2016) %>% mutate(y_pos = c(3.1e4, 1.1e4, 1.8e4)), aes(y = y_pos, label = place_of_death), hjust = 0) +
  geom_text(data = ~filter(.x, year==2021), aes(x=2021.1, y=number_of_deaths, label="*"), inherit.aes = FALSE) +
  scale_colour_viridis_d(option="C", end = 0.8, guide = FALSE) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_x_continuous(breaks = 2015:2021) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.box="vertical",
    legend.margin=margin()
    ) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ","), limits = c(0, NA)) +
  labs(
    x = "Year", y = "Deaths (N)",
    subtitle = paste0("* ",only_2021_text),
    caption = paste0(c(death_registrations_text,source_nrs_text), collapse="\n")
  ) +
  NULL
)

@@

### Only up to incl. 2020

```{r}
(figure_number_of_deaths_by_place_by_year_2020 <-
  bind_rows(
    proportions_of_historical_deaths_by_place %>% filter(year==2019) %>% mutate(covid_status = "Non Covid-19 deaths"),  # add extra rows of 2019 data for plotting line between 2019 and 2020
    proportions_of_historical_deaths_by_place %>% mutate(covid_status = "All deaths"),
    proportions_of_current_non_covid_deaths_by_place %>% mutate(covid_status = "Non Covid-19 deaths"),
    proportions_of_current_deaths_by_place %>% mutate(covid_status = "All deaths")
  ) %>%
  filter(!place_of_death %in% c("All","Other")) %>%  # don't show Other
  filter(year != 2021) %>%  # don't include 2021
  mutate(
    place_of_death = factor(x = place_of_death, levels = order_of_place_of_death_levels[c(1,3,2,4)])   # move home to 2nd position to match order in plot
    ) %>%
  ggplot(., aes(x=year, y=number_of_deaths, colour = place_of_death)) +
  geom_line(data = . %>% filter(covid_status == "All deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_line(data = . %>% filter(covid_status == "Non Covid-19 deaths"), aes(group = place_of_death, linetype = covid_status)) +
  geom_point(data = . %>% filter(!covid_status=="Non Covid-19 deaths" | !year==2019)) +
  geom_text(data = . %>% filter(year==2016) %>% mutate(y_pos = c(3.1e4, 1.1e4, 1.8e4)), aes(y = y_pos, label = place_of_death), hjust = 0) +
  scale_colour_viridis_d(option="C", end = 0.8, guide = FALSE) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_x_continuous(breaks = 2015:2021) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.box="vertical",
    legend.margin=margin()
    ) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ","), limits = c(0, NA)) +
  labs(
    x = "Year", y = "Deaths (N)",
    caption = paste0(c(death_registrations_text,source_nrs_text), collapse="\n")
  ) +
  NULL
)

save_output_file(filename = paste0(dir_outputs,"/figure_number_of_deaths_by_place_by_year_2020"), extensions = c(".pdf",".svg",".png"), plot = figure_number_of_deaths_by_place_by_year_2020, width = 15, height = 11, dpi = 300, units = "cm")
```
